% =========================================================
% Required packages
% \usepackage{amsmath,amssymb,amsfonts,bm}
% \usepackage{algorithm}
% \usepackage{algpseudocode}
% =========================================================

\subsection{Variable-Cardinality Bidirectional Super-Node Alignment}

Given two images, we first coarsen their patch graphs into super-node graphs
with possibly different numbers of nodes:
\[
G^A=(V^A,W^A), \qquad G^B=(V^B,W^B),
\]
where \(W^A \in \mathbb{R}^{n_A \times n_A}\) and
\(W^B \in \mathbb{R}^{n_B \times n_B}\), with \(n_A\) and \(n_B\) not
necessarily equal.
Let
\[
Z^A = [z_1^A,\dots,z_{n_A}^A]^\top \in \mathbb{R}^{n_A \times d},
\qquad
Z^B = [z_1^B,\dots,z_{n_B}^B]^\top \in \mathbb{R}^{n_B \times d}
\]
denote the corresponding super-node features.

\paragraph{Cross-graph soft transport.}
To align graphs with different cardinalities, we compute a soft cross-graph
transport from node similarities:
\[
S_{ij} = \mathrm{sim}(z_i^A, z_j^B),
\]
where \(\mathrm{sim}(\cdot,\cdot)\) can be cosine similarity or dot product.

We then define two directional transport matrices:
\begin{align}
P^{A\leftarrow B}_{ij}
&=
\frac{\exp(S_{ij}/\tau_p)}
{\sum\limits_{k=1}^{n_B}\exp(S_{ik}/\tau_p)}
\in \mathbb{R}^{n_A \times n_B}, \\
P^{B\leftarrow A}_{ji}
&=
\frac{\exp(S_{ij}/\tau_p)}
{\sum\limits_{k=1}^{n_A}\exp(S_{kj}/\tau_p)}
\in \mathbb{R}^{n_B \times n_A},
\end{align}
where \(\tau_p>0\) is a temperature parameter.
The forward transport \(P^{A\leftarrow B}\) maps graph \(B\) into the
coordinate system of graph \(A\), while \(P^{B\leftarrow A}\) provides the
reverse mapping. This bidirectional design explicitly removes the asymmetry of
one-sided transport.

\paragraph{Direct node alignment.}
To impose direct supervision on node correspondence, we align transported
super-node features in both directions:
\begin{equation}
\mathcal{L}_{\mathrm{node}}^{\mathrm{bi}}
=
\left\| Z^A - P^{A\leftarrow B} Z^B \right\|_F^2
+
\left\| Z^B - P^{B\leftarrow A} Z^A \right\|_F^2.
\end{equation}

\paragraph{Bidirectional local edge consistency.}
We further align first-order graph relations under both transports:
\begin{equation}
\mathcal{L}_{\mathrm{edge}}^{\mathrm{bi}}
=
\left\| W^A - P^{A\leftarrow B} W^B (P^{A\leftarrow B})^\top \right\|_F^2
+
\left\| W^B - P^{B\leftarrow A} W^A (P^{B\leftarrow A})^\top \right\|_F^2.
\end{equation}

\paragraph{Final objective.}
Our final objective augments any base matching loss
\(\mathcal{L}_{\mathrm{base}}\) with direct node alignment and local
structural regularization:
\begin{equation}
\mathcal{L}_{\mathrm{total}}
=
\mathcal{L}_{\mathrm{base}}
+
\lambda_n \mathcal{L}_{\mathrm{node}}^{\mathrm{bi}}
+
\lambda_e \mathcal{L}_{\mathrm{edge}}^{\mathrm{bi}},
\end{equation}
where \(\lambda_n,\lambda_e \ge 0\) control the strengths of node and
local-edge alignment, respectively.

\paragraph{Remark.}
This simplified variant is sufficient for our setting: it supports graphs with
different numbers of super-nodes while enforcing both direct node-level
alignment and first-order structural consistency, without introducing
additional higher-order path regularization.

\begin{algorithm}[t]
\caption{Variable-Cardinality Bidirectional Super-Node Alignment}
\label{alg:bidirectional_supernode_alignment}
\begin{algorithmic}[1]
\Require
Patch features \(X^A, X^B\);
target super-node counts \(n_A, n_B\);
temperature \(\tau_p\);
weights \(\lambda_n,\lambda_e\)
\Ensure
\(\mathcal{L}_{\mathrm{total}}\)

\State \((Z^A, W^A) \gets \mathrm{CoarsenGraph}(X^A, n_A)\)
\State \((Z^B, W^B) \gets \mathrm{CoarsenGraph}(X^B, n_B)\)

\For{$i=1$ to $n_A$}
    \For{$j=1$ to $n_B$}
        \State \(S_{ij} \gets \mathrm{sim}(z_i^A, z_j^B)\)
    \EndFor
\EndFor

\State Compute forward transport:
\[
P^{A\leftarrow B}_{ij}
=
\frac{\exp(S_{ij}/\tau_p)}
{\sum_{k=1}^{n_B}\exp(S_{ik}/\tau_p)}
\]
\State Compute reverse transport:
\[
P^{B\leftarrow A}_{ji}
=
\frac{\exp(S_{ij}/\tau_p)}
{\sum_{k=1}^{n_A}\exp(S_{kj}/\tau_p)}
\]

\State
\(
\mathcal{L}_{\mathrm{node}}^{\mathrm{bi}}
\gets
\| Z^A - P^{A\leftarrow B} Z^B \|_F^2
+
\| Z^B - P^{B\leftarrow A} Z^A \|_F^2
\)

\State
\(
\mathcal{L}_{\mathrm{edge}}^{\mathrm{bi}}
\gets
\| W^A - P^{A\leftarrow B} W^B (P^{A\leftarrow B})^\top \|_F^2
+
\| W^B - P^{B\leftarrow A} W^A (P^{B\leftarrow A})^\top \|_F^2
\)

\State
\(
\mathcal{L}_{\mathrm{total}}
\gets
\mathcal{L}_{\mathrm{base}}
+
\lambda_n \mathcal{L}_{\mathrm{node}}^{\mathrm{bi}}
+
\lambda_e \mathcal{L}_{\mathrm{edge}}^{\mathrm{bi}}
\)

\State \Return \(\mathcal{L}_{\mathrm{total}}\)
\end{algorithmic}
\end{algorithm}